---
title: "Statistical Power Many Labs Projects"
author: "Robbie C.M. van Aert"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(kableExtra)

load("res.RData")
```

This report is based on the code "power_ml_2.R" ["power_ml_2.R"](NOG TOEVOEGEN) for computing the statistical power for Many Labs projects. The $I^2$-statistic (i.e., proportion of total variance in a meta-analysis that can be attributed to between-study variance in true effect size) and statistical power for testing the null-hypothesis of no effect and the null-hypothesis of homogeneous true effect size (*Q*-test) are presented below. $\rho$ refers to the intra-class correlation and $\mu$ is the true effect size. Statistical power above the threshold of 0.8 is colored green and below 0.8 is colored red.

<div style="margin-top:50px;">

### $I^2$-statistic

```{r I2}
tab <- colMeans(res$mean_I2)

kable(t(tab), escape = FALSE, digits = 1) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), 
                full_width = FALSE) %>%
  add_header_above(c("$\\rho$" = ncol(t(tab))))
  


```

</div>

<div style="margin-top:50px;">

### Statistical power for testing null-hypothesis of no effect

```{r pow_mu}
tab <- cbind(rownames(res$pow_mu), round(res$pow_mu, 3))
rownames(tab) <- rep("$\\mu$", nrow(tab))

tab[ ,2:ncol(tab)] <- cell_spec(tab[ ,2:ncol(tab)], "html", 
                                color = ifelse(as.numeric(tab[ ,2:ncol(tab)]) > 0.8, 
                                               "green", "red"))

kable(tab, escape = FALSE) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), 
                full_width = FALSE) %>%
  add_header_above(c(" " = 2, "$\\rho$" = ncol(tab)-1)) %>%
  column_spec(2, bold = TRUE) %>%
  collapse_rows(columns = 1, latex_hline = "major")
 
```

</div>

<div style="margin-top:50px;">

### Statistical power for testing whether true effect size is homogeneous

```{r pow_tau2}
tab <- cbind(rownames(res$pow_tau2), round(res$pow_tau2, 3))
rownames(tab) <- rep("$\\mu$", nrow(tab))

tab[ ,2:ncol(tab)] <- cell_spec(tab[ ,2:ncol(tab)], "html", 
                                color = ifelse(as.numeric(tab[ ,2:ncol(tab)]) > 0.8, 
                                               "green", "red"))

kable(tab, escape = FALSE) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), 
                full_width = FALSE) %>%
  add_header_above(c(" " = 2, "$\\rho$" = ncol(tab)-1)) %>%
  column_spec(2, bold = TRUE) %>%
  collapse_rows(columns = 1, latex_hline = "major")
 
```

</div>